---
title: 'Task 24: The US Grocer (KR)'
author: "Adam Nielsen"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: center
resource_files:
- task_24-NIELSEN-.html
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(dygraphs)
library(tidyquant)
#library(quantmod)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!
KRstock <- tq_get("KR")
```

## Background

_Place Task Background Here_

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!
KRstock <- KRstock %>%
  filter("date" > "2016-03-24")

stock_xts <- timetk::tk_xts(
  data = KRstock, 
  select = c(open, high, low,close), 
  date_var = date
)
```

## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!
dygraph(stock_xts, main = "Kroger Stock") %>%  
  dyRebase(value = 10000) %>%
  dyRangeSelector(dateWindow = c("2016-03-24", "2021-03-24")) %>%
  dyAnnotation("2017-6-15", text = "B", tooltip = "Poor quarterly report, Amazon acquired Wholefoods") %>%
  dyAnnotation("2015-12-29", text = "A", tooltip = "All-time hight closing price") %>%
  dyAnnotation("2018-06-28", text = "C", tooltip = "Autonomous Delivery Announcement")
  
```

## Conclusions
Krogers stalk peaked just over 4 years ago. it began to decline and reached low points in October of 2017 and July of 2019 but appears to be recovering again. Most of the big ups and downs in stalk price coincide with Quarterly and yearly reports released by Kroger.

There where a few points I found interesting. Point [B] is when Kroger released a poor quarterly report that also coinsided with Amazon buying wholefoods. Point C is when Kroger released a partnership with a autonomous vehicle company with plans to develop a autonomous grocery delivery service.