---
title: "Exploratory Data Analysis"
author: "YOUR NAME"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Reading Notes

- EDA = Exploratory Data Analysis
- “Far better an approximate answer to the right question, which is often vague, than an exact answer to the wrong question, which can always be made precise.” — John Tukey

2 main questions  
- What type of variation occurs within my variables?  
- What type of covariation occurs between my variables?  

**Variation**  
categorical bar chart  
*ggplot(data = diamonds) +*  
  *geom_bar(mapping = aes(x = cut))*  
  
count the number in each category  
*diamonds %>%*  
  *count(cut)*  
  
continuous histogram  
*ggplot(data = diamonds) +*  
  *geom_histogram(mapping = aes(x = carat), binwidth = 0.5)*  
  
continuous count using "bins"  
*diamonds %>% *  
 *count(cut_width(carat, 0.5))*  
 
overlapping histograms use freqpoly for better visualization  
*ggplot(data = smaller, mapping = aes(x = carat, colour = cut)) +*  
  *geom_freqpoly(binwidth = 0.1)*  
  
- Which values are the most common? Why?  
- Which values are rare? Why? Does that match your expectations?  
- Can you see any unusual patterns? What might explain them?  

zoom into a plot with coord_cartesian  
*ggplot(diamonds) +*   
  *geom_histogram(mapping = aes(x = y), binwidth = 0.5) +*  
  *coord_cartesian(ylim = c(0, 50))*  

replace bad data using mutate and ifelse  
*diamonds2 <- diamonds %>% *  
  *mutate(y = ifelse(y < 3 | y > 20, NA, y))*  

-Why are these values missing?  
*mutate df to make seperate category?*  

**Covariation**  
use a density plot to standardize data between categories  
*ggplot(data = diamonds, mapping = aes(x = price, y = ..density..)) +   
  geom_freqpoly(mapping = aes(colour = cut), binwidth = 500)*  
  
boxplots are cool  
*ggplot(data = diamonds, mapping = aes(x = cut, y = price)) +  
  geom_boxplot()*
  



## EDA Example

The code below is an example of the EDA process using the `starwars` data from the `tidyverse` package. (Make sure you have the `tidyverse` package installed!)

Run the code line-by-line and look at the output. Add a comment to each line of code that explains what it does/what insights it provides.

```{r}
library(tidyverse)

dim(starwars) #returns the dimensions of starwars
colnames(starwars) # returns the column names of starwars

head(starwars) # a small preview of the df
glimpse(starwars) # the df by column

?starwars # help and info about df, opens up a html page

starwars %>% count(species) # a count of each species in df

mean(starwars$height) #the mean of all heights
mean(starwars$height, na.rm = TRUE) # the mean of all heights not counting NA values

summary(starwars$height) #basic info for df (min mean max NA count etc)

# a function that takes in cm and returns the equivelent length in feet
cm_to_ft <- function(cm){ 
  ft = cm / 30.48
  return(ft)
}

#uses cm_to_feet to create a new variable height_ft in df
starwars_2 <- starwars %>% mutate(height_ft = cm_to_ft(height)) 

dim(starwars_2)
colnames(starwars_2)

summary(starwars_2$height_ft)

#a histogram of height_ft
ggplot(starwars_2, aes(height_ft)) + 
  geom_histogram()

#filter to find the tallest row, na.rm is needed
starwars_2 %>% filter(height_ft == max(height_ft))
starwars_2 %>% filter(height_ft == max(height_ft, na.rm = TRUE))

# https://starwars.fandom.com/wiki/Yarael_Poof
```

## EDA Practice

Continue exploring the `starwars` data to gain additional insights, using [R4DS: Chapter 7](https://r4ds.had.co.nz/exploratory-data-analysis.html) as a guide.

It is ok if you don't understand the all code in Chapter 7. (That is what we'll be learning the next two weeks!) If writing your own code is a struggle, try the "copy, paste, and tweak" method.

```{r}
# your code goes here
```